---
title: "Take-Home Exercise 1"
description: |
  In this Takehome Exercise, I will explore...
author:
  - name: Yeo Kim Siang
    url: https://www.linkedin.com/in/kim-siang-yeo-b42317134/
    affiliation: School of Life
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

In this take-home exercise, you are required to apply ... 

# Getting Started 

Before we get started, ...

Otherwise the code chunk below will do the trick. 

```{r}
packages = c('tidyverse')

for (p in packages){ 
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
  }
```

# Importing Data 

The code chunk below imports *Participants.csv* from the data sub-folder into R by using [`read_csv()`](https://www.rdocumentation.org/packages/readr/versions/1.3.1) of [**readr**](https://www.rdocumentation.org/packages/readr/versions/1.3.1), and saves it as a tibble dataframe called *participant_data*. 

```{r}
participant_data <- read_csv("data/Participants.csv")
```

# Simple Data Chart

The code chunk below plots a bar chart by using geom_bar() of ggplot2. 

```{r}
ggplot(data = participant_data, 
       aes(x = educationLevel)) + 
  geom_bar()
```





